---
title: My dynamic report
output: html_fragment
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```
```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
}
h2 {
  color: #2c3e50;
}
```

## My eating and drinking habits

This report analyses my personal eating and drinking observations recorded over several days. The data includes what I consumed, where it came from, how long each occasion took, and how hungry I was beforehand.
```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRVF9Y5x_cYuEhx6uxgw-_FSC8g9ZhleAA-obB7GmTNm90Td9KOT54zMAFkb2p7xRqxrpoHUKJhFQdD/pub?gid=863542806&single=true&output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    score = Score,
    hunger_score = `How hungry were you before eating/drinking occasion? (1 = not hungry at all, 10 = extremely hungry)`,
    food_type = `What type of food / drink did you primarily consume?`,
    food_source = `Where did the food/drink come from?`,
    duration = `Approximately how many minutes did this eating / drinking occasion take?`,
    time_of_day = `What time of day was this observation?`
  )

mean_hunger <- round(mean(latest_data$hunger_score, na.rm = TRUE), 1)
mean_duration <- round(mean(latest_data$duration, na.rm = TRUE), 1)
total_obs <- length(latest_data$hunger_score)
```

Across `r total_obs` observations, my average hunger score before eating or drinking was `r mean_hunger` out of 10, and the average duration of each occasion was `r mean_duration` minutes.
```{r}
ggplot(latest_data, aes(x = food_type)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Types of food/drink consumed",
       x = "Food/drink type",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
ggplot(latest_data, aes(x = food_source)) +
  geom_bar(fill = "coral") +
  labs(title = "Where food/drink came from",
       x = "Source",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
